
         
             family =binomial(link = "logit"), 
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [4] 
ci.ul
table(model.1$model$preecl) 


model.1<-glm(preecl~(PFHxS.iqr), 
             family =binomial(link = "logit"), 
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [4] 
ci.ul
table(model.1$model$preecl) 


model.1<-glm(preecl~(PFNA.iqr), 
             family =binomial(link = "logit"), 
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [4] 
ci.ul
table(model.1$model$preecl) 


# gestational hypertension 

model.1<-glm(g_htn~(PFOA.iqr), 
             family =binomial(link = "logit"), 
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [4] 
ci.ul
table(model.1$model$g_htn) 


model.1<-glm(g_htn~(PFOS.iqr), 
             family =binomial(link = "logit"), 
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [4] 
ci.ul
table(model.1$model$g_htn) 


model.1<-glm(g_htn~(PFHxS.iqr), 
             family =binomial(link = "logit"), 
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [4] 
ci.ul
table(model.1$model$g_htn) 


model.1<-glm(g_htn~(PFNA.iqr), 
             family =binomial(link = "logit"), 
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [4] 
ci.ul
table(model.1$model$g_htn) 



# adjusted ORs 

# preeclampsisa 

model.1<-glm(preecl~(PFOA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             family =binomial(link = "logit"), 
             data=df2) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2] 
ci.ul
table(model.1$model$preecl) 


model.1<-glm(preecl~(PFOS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             family =binomial(link = "logit"), 
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$preecl) 

model.1<-glm(preecl~(PFHxS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             family =binomial(link = "logit"), 
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$preecl) 
######################################### 


model.1<-glm(preecl~(PFNA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             family =binomial(link = "logit"), 
             data=df2) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$preecl) 



# gestational hypertension 

model.1<-glm(g_htn~(PFOA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             
             family =binomial(link = "logit"), 
             
             data=df2) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2] 
ci.ul
table(model.1$model$g_htn) 


model.1<-glm(g_htn~(PFOS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             family =binomial(link = "logit"), 
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$g_htn) 


model.1<-glm(g_htn~(PFHxS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             family =binomial(link = "logit"), 
             
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$g_htn) 


model.1<-glm(g_htn~(PFNA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             family =binomial(link = "logit"), 
             data=df2) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$g_htn) 



```

## Table S2
Sensitivity analysis using full term births (i.e., births occurring at gestational age ≥39 weeks and without complications, such as gestational hypertension, gestational diabetes, or preeclampsia) as the reference group when estimating odds ratios and 95% confidence intervals for the association between hypertensive disorders of pregnancy and individual PFAS and their mixture among pregnant persons in the Atlanta African American Maternal-Child Cohort, 2014-2020
```{r}
##### quantile g-compuation ####

## Subset out complete cases, do this for both preeclampsia and gestational hypertension
## Creates one dataset for each outcome 
df.cases.preeclampsia.se<-c('mat_educ', 
                         'mat_age', 
                         'ppbmi', 
                         'parity', 
                         'alc.smoke', 
                         "log.PFNA", 
                         "log.PFOA", 
                         "log.PFOS", 
                         "log.PFHxS", 
                         'preecl_hftb') 



df.mixtures.preec.se<-df2[df.cases.preeclampsia.se]  
df.mixtures.preec.se<-df.mixtures.preec.se[complete.cases(df.mixtures.preec.se),] 


df.cases.ghtn.se<-c('mat_educ', 
                 'mat_age', 
                 'ppbmi', 
                 'parity', 
                 'alc.smoke', 
                 "log.PFNA", 
                 "log.PFOA", 
                 "log.PFOS", 
                 "log.PFHxS", 
                 'g_htn_hftb') 

df.mixtures.ghtn.se<-df2[df.cases.ghtn.se]  
df.mixtures.ghtn.se<-df.mixtures.ghtn.se[complete.cases(df.mixtures.ghtn.se),] 


## Set names of exposure variables 
Xmn.chem<-c("log.PFNA", "log.PFOA", "log.PFOS","log.PFHxS")  


### Run qgcomp model for preeclampsia 

Mixture<- qgcomp.noboot(preecl_hftb ~ log.PFNA + log.PFOA + log.PFOS +  log.PFHxS + 
                          as.factor(mat_educ) + mat_age + as.factor(parity) + as.factor(alc.smoke) + ppbmi, 
                        expnms = Xmn.chem, 
                        data= df.mixtures.preec.se, 
                        family=binomial(), 
                        q=4) 


# Ouput weight plot
plot(Mixture)  
# Output effect estimates  
exp(round((Mixture $psi),2))  
exp(round((Mixture $ci.coef),2)) 
table(df.mixtures.preec.se$preecl) 

#negative weights: 
Mixture$neg.weights 
# positive weights: 
Mixture$pos.weights 


### Run qgcomp model for gestational hypertension  

Mixture<- qgcomp.noboot(g_htn_hftb ~ log.PFNA + log.PFOA + log.PFOS +  log.PFHxS + 
                          as.factor(mat_educ) + mat_age + as.factor(parity) + as.factor(alc.smoke) + ppbmi, 
                        expnms = Xmn.chem, 
                        data= df.mixtures.ghtn.se, 
                        family=binomial(), 
                        q=4) 


# Ouput weight plot
plot(Mixture)  
# Output effect estimates  
exp(round((Mixture $psi),2))  
exp(round((Mixture $ci.coef),2)) 
table(df.mixtures.ghtn.se$g_htn_hftb)


# individual ORs - preeclampsisa 

model.1<-glm(preecl_hftb~(PFOA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             
             family =binomial(link = "logit"), 
             
             data=df2) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll

ci.ul<-round(exp(confint(model.1)),2) [2,2] 
ci.ul
table(model.1$model$preecl_hftb) 


model.1<-glm(preecl_hftb~(PFOS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             family =binomial(link = "logit"), 
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$preecl_hftb) 


model.1<-glm(preecl_hftb~(PFHxS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             family =binomial(link = "logit"), 
             
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$preecl_hftb) 


model.1<-glm(preecl_hftb~(PFNA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             family =binomial(link = "logit"), 
             data=df2) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$preecl_hftb) 



#individual ORs - gestational hypertension 

model.1<-glm(g_htn_hftb~(PFOA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             
             family =binomial(link = "logit"), 
             
             data=df2) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2] 
ci.ul
table(model.1$model$g_htn_hftb) 


model.1<-glm(g_htn_hftb~(PFOS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             family =binomial(link = "logit"), 
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$g_htn_hftb) 


model.1<-glm(g_htn_hftb~(PFHxS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             family =binomial(link = "logit"), 
             
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$g_htn_hftb) 


model.1<-glm(g_htn_hftb~(PFNA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             family =binomial(link = "logit"), 
             data=df2) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$g_htn_hftb) 


```

## Table S3
Weights representing the proportion of the positive and negative effect on hypertensive disorders of pregnancy in relation to a mixture of PFAS, estimated using quantile g-computation in the Atlanta African American Maternal-Child Cohort, 2014-2020 (N=513)
```{r}

df2$log.PFNA<-log(df2$impPFNA)  
df2$log.PFOA<-log(df2$impPFOA)  
df2$log.PFOS<-log(df2$impPFOS)  
df2$log.PFHxS<-log(df2$impPFHxS) 


## Subset out complete cases, do this for both preeclampsia and gestational hypertension
## Creates one dataset for each outcome 
df.cases.preeclampsia<-c('mat_educ', 
            'mat_age', 
            'ppbmi', 
            'parity', 
            'alc.smoke', 
            "log.PFNA", 
            "log.PFOA", 
            "log.PFOS", 
            "log.PFHxS", 
            'preecl') 



df.mixtures.preec<-df2[df.cases.preeclampsia]  
df.mixtures.preec<-df.mixtures.preec[complete.cases(df.mixtures.preec),] 


df.cases.ghtn<-c('mat_educ', 
                         'mat_age', 
                         'ppbmi', 
                         'parity', 
                         'alc.smoke', 
                         "log.PFNA", 
                         "log.PFOA", 
                         "log.PFOS", 
                         "log.PFHxS", 
                         'g_htn') 

df.mixtures.ghtn<-df2[df.cases.ghtn]  
df.mixtures.ghtn<-df.mixtures.ghtn[complete.cases(df.mixtures.ghtn),] 


## Set names of exposure variables 
Xmn.chem<-c("log.PFNA", "log.PFOA", "log.PFOS","log.PFHxS")  


### Run qgcomp model for preeclampsia 

Mixture<- qgcomp.noboot(preecl ~ log.PFNA + log.PFOA + log.PFOS +  log.PFHxS + 
                          as.factor(mat_educ) + mat_age + as.factor(parity) + as.factor(alc.smoke) + ppbmi, 
                        expnms = Xmn.chem, 
                        data= df.mixtures.preec, 
                        family=binomial(), 
                        q=4) 
# Ouput weight plot
plot(Mixture)  
# Output effect estimates  
exp(round((Mixture $psi),2))  
exp(round((Mixture $ci.coef),2)) 
table(df.mixtures.preec$preecl) 

#negative weights: 
Mixture$neg.weights 
# positive weights: 
Mixture$pos.weights 


### Run qgcomp model for gestational hypertension  

Mixture<- qgcomp.noboot(g_htn ~ log.PFNA + log.PFOA + log.PFOS +  log.PFHxS + 
                          as.factor(mat_educ) + mat_age + as.factor(parity) + as.factor(alc.smoke) + ppbmi, 
                        expnms = Xmn.chem, 
                        data= df.mixtures.ghtn, 
                        family=binomial(), 
                        q=4) 

# Ouput weight plot
plot(Mixture)  
# Output effect estimates  
exp(round((Mixture $psi),2))  
exp(round((Mixture $ci.coef),2)) 
table(df.mixtures.ghtn$g_htn) 

#negative weights: 
Mixture$neg.weights 
# positive weights: 
Mixture$pos.weights 

```

## Table S4
Sensitivity analysis additionally removing those with chronic pre-pregnancy hypertension when estimating odds ratios and 95% confidence intervals for the association between hypertensive disorders of pregnancy and individual PFAS and their mixture among pregnant persons in the Atlanta African American Maternal-Child Cohort, 2014-2020
```{r}
df.no.chtn<-df2[which(df2$c_htn!=1),]

## Subset out complete cases, do this for both preeclampsia and gestational hypertension
## Creates one dataset for each outcome 
df.cases.preeclampsia.se.2<-c('mat_educ', 
                              'mat_age', 
                              'ppbmi', 
                              'parity', 
                              'alc.smoke', 
                              "log.PFNA", 
                              "log.PFOA", 
                              "log.PFOS", 
                              "log.PFHxS", 
                              'preecl') 



df.cases.preeclampsia.se.2<-df.no.chtn[df.cases.preeclampsia.se.2]  
df.cases.preeclampsia.se.2<-df.cases.preeclampsia.se.2[complete.cases(df.cases.preeclampsia.se.2),] 


df.cases.ghtn.se.2<-c('mat_educ', 
                      'mat_age', 
                      'ppbmi', 
                      'parity', 
                      'alc.smoke', 
                      "log.PFNA", 
                      "log.PFOA", 
                      "log.PFOS", 
                      "log.PFHxS", 
                      'g_htn') 

df.cases.ghtn.se.2<-df.no.chtn[df.cases.ghtn.se.2]  
df.cases.ghtn.se.2<-df.cases.ghtn.se.2[complete.cases(df.cases.ghtn.se.2),] 


## Set names of exposure variables 
Xmn.chem<-c("log.PFNA", "log.PFOA", "log.PFOS","log.PFHxS")  


### Run qgcomp model for preeclampsia 

Mixture<- qgcomp.noboot(preecl ~ log.PFNA + log.PFOA + log.PFOS +  log.PFHxS + 
                          as.factor(mat_educ) + mat_age + as.factor(parity) + as.factor(alc.smoke) + ppbmi , 
                        expnms = Xmn.chem, 
                        data= df.cases.preeclampsia.se.2, 
                        family=binomial(), 
                        q=4) 

# Output effect estimates  
exp(round((Mixture $psi),2))  
exp(round((Mixture $ci.coef),2)) 
table(df.cases.preeclampsia.se.2$preecl)

### Run qgcomp model for gestational hypertension  

Mixture<- qgcomp.noboot(g_htn ~ log.PFNA + log.PFOA + log.PFOS +  log.PFHxS + 
                          as.factor(mat_educ) + mat_age + as.factor(parity) + as.factor(alc.smoke) + ppbmi , 
                        expnms = Xmn.chem, 
                        data= df.cases.ghtn.se.2, 
                        family=binomial(), 
                        q=4) 


# Output effect estimates  
exp(round((Mixture $psi),2))  
exp(round((Mixture $ci.coef),2)) 
table(df.cases.ghtn.se.2$g_htn)




# adjusted ORs removing those with chtn

# preeclampsisa 

df.no.chtn$PFOA.iqr<-log(df.no.chtn$impPFOA)/IQR(log(df.no.chtn$impPFOA),na.rm=TRUE) 
model.1<-glm(preecl~(PFOA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi , 
             
             family =binomial(link = "logit"), 
             
             data=df.no.chtn) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2] 
ci.ul
table(model.1$model$preecl) 


df.no.chtn$PFOS.iqr<-log(df.no.chtn$impPFOS)/IQR(log(df.no.chtn$impPFOS),na.rm=TRUE) 
model.1<-glm(preecl~(PFOS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi, 
             family =binomial(link = "logit"), 
             data=df.no.chtn) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$preecl) 


df.no.chtn$PFHxS.iqr<-log(df.no.chtn$impPFHxS)/IQR(log(df.no.chtn$impPFHxS),na.rm=TRUE) 
model.1<-glm(preecl~(PFHxS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi , 
             family =binomial(link = "logit"), 
             
             data=df.no.chtn) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$preecl) 

df.no.chtn$PFNA.iqr<-log(df.no.chtn$impPFNA)/IQR(log(df.no.chtn$impPFNA),na.rm=TRUE) 

model.1<-glm(preecl~(PFNA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi , 
             family =binomial(link = "logit"), 
             data=df.no.chtn) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$preecl) 



# gestational hypertension 

df.no.chtn$PFOA.iqr<-log(df.no.chtn$impPFOA)/IQR(log(df.no.chtn$impPFOA),na.rm=TRUE) 
model.1<-glm(g_htn~(PFOA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi , 
             
             family =binomial(link = "logit"), 
             
             data=df.no.chtn) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2] 
ci.ul
table(model.1$model$g_htn) 


df.no.chtn$PFOS.iqr<-log(df.no.chtn$impPFOS)/IQR(log(df.no.chtn$impPFOS),na.rm=TRUE) 
model.1<-glm(g_htn~(PFOS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi , 
             family =binomial(link = "logit"), 
             data=df.no.chtn) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$g_htn) 


df.no.chtn$PFHxS.iqr<-log(df.no.chtn$impPFHxS)/IQR(log(df.no.chtn$impPFHxS),na.rm=TRUE) 
model.1<-glm(g_htn~(PFHxS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi , 
             family =binomial(link = "logit"), 
             
             data=df.no.chtn) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$g_htn) 


df.no.chtn$PFNA.iqr<-log(df.no.chtn$impPFNA)/IQR(log(df.no.chtn$impPFNA),na.rm=TRUE) 

model.1<-glm(g_htn~(PFNA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi , 
             family =binomial(link = "logit"), 
             data=df.no.chtn) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$g_htn) 



```

## Table S5
Sensitivity analysis additionally adjusting for experiences of gendered racial stress when estimating odds ratios and 95% confidence intervals for the association between hypertensive disorders of pregnancy and individual PFAS and their mixture among pregnant persons in the Atlanta African American Maternal-Child Cohort, 2014-2020
```{r}
##### quantile g-compuation ####


## Subset out complete cases, do this for both preeclampsia and gestational hypertension
## Creates one dataset for each outcome 
df.cases.preeclampsia.se.1<-c('mat_educ', 
                            'mat_age', 
                            'ppbmi', 
                            'parity', 
                            'alc.smoke', 
                            "log.PFNA", 
                            "log.PFOA", 
                            "log.PFOS", 
                            "log.PFHxS", 
                            'preecl',
                            'JHP_Total') 



df.cases.preeclampsia.se.1<-df2[df.cases.preeclampsia.se.1]  
df.cases.preeclampsia.se.1<-df.cases.preeclampsia.se.1[complete.cases(df.cases.preeclampsia.se.1),] 


df.cases.ghtn.se.1<-c('mat_educ', 
                    'mat_age', 
                    'ppbmi', 
                    'parity', 
                    'alc.smoke', 
                    "log.PFNA", 
                    "log.PFOA", 
                    "log.PFOS", 
                    "log.PFHxS", 
                    'g_htn',
                    'JHP_Total') 

df.cases.ghtn.se.1<-df2[df.cases.ghtn.se.1]  
df.cases.ghtn.se.1<-df.cases.ghtn.se.1[complete.cases(df.cases.ghtn.se.1),] 


## Set names of exposure variables 
Xmn.chem<-c("log.PFNA", "log.PFOA", "log.PFOS","log.PFHxS")  


### Run qgcomp model for preeclampsia 

Mixture<- qgcomp.noboot(preecl ~ log.PFNA + log.PFOA + log.PFOS +  log.PFHxS + 
                          as.factor(mat_educ) + mat_age + as.factor(parity) + as.factor(alc.smoke) + ppbmi + JHP_Total, 
                        expnms = Xmn.chem, 
                        data= df.cases.preeclampsia.se.1, 
                        family=binomial(), 
                        q=4) 

# Output effect estimates  
exp(round((Mixture $psi),2))  
exp(round((Mixture $ci.coef),2)) 
table(df.cases.preeclampsia.se.1$preecl)

### Run qgcomp model for gestational hypertension  

Mixture<- qgcomp.noboot(g_htn ~ log.PFNA + log.PFOA + log.PFOS +  log.PFHxS + 
                          as.factor(mat_educ) + mat_age + as.factor(parity) + as.factor(alc.smoke) + ppbmi + JHP_Total, 
                        expnms = Xmn.chem, 
                        data= df.cases.ghtn.se.1, 
                        family=binomial(), 
                        q=4) 


# Output effect estimates  
exp(round((Mixture $psi),2))  
exp(round((Mixture $ci.coef),2)) 
table(df.cases.ghtn.se.1$g_htn)




# adjusted individual ORs additionally adjusting for JHP 

# preeclampsisa 

model.1<-glm(preecl~(PFOA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi + JHP_Total, 
             
             family =binomial(link = "logit"), 
             
             data=df2) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2] 
ci.ul
table(model.1$model$preecl) 


model.1<-glm(preecl~(PFOS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi + JHP_Total, 
             family =binomial(link = "logit"), 
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$preecl) 


model.1<-glm(preecl~(PFHxS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi + JHP_Total, 
             family =binomial(link = "logit"), 
             
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$preecl) 


model.1<-glm(preecl~(PFNA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi + JHP_Total, 
             family =binomial(link = "logit"), 
             data=df2) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$preecl) 



# gestational hypertension 

model.1<-glm(g_htn~(PFOA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi + JHP_Total, 
             
             family =binomial(link = "logit"), 
             
             data=df2) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2] 
ci.ul
table(model.1$model$g_htn) 


model.1<-glm(g_htn~(PFOS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi + JHP_Total, 
             family =binomial(link = "logit"), 
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$g_htn) 


model.1<-glm(g_htn~(PFHxS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi + JHP_Total, 
             family =binomial(link = "logit"), 
             
             data=df2) 

or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$g_htn) 


model.1<-glm(g_htn~(PFNA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi + JHP_Total, 
             family =binomial(link = "logit"), 
             data=df2) 
or<-round(exp(coef(model.1)),2) 
or 
ci.ll<-round(exp(confint(model.1)),2) [2] 
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]  
ci.ul
table(model.1$model$g_htn) 



```

## Table S6
Sensitivity analysis estimating odds ratios and 95% confidence intervals for the association between hypertensive disorders of pregnancy (any versus none) and individual PFAS and their mixture among pregnant persons in the Atlanta African American Maternal-Child Cohort, 2014-2020
```{r}
model.1<-glm(HDP~(PFOA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi,
             family =binomial(link = "logit"),
             data=df2)
or<-round(exp(coef(model.1)),2)
or
ci.ll<-round(exp(confint(model.1)),2) [2]
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]
ci.ul
table(model.1$model$HDP)
#0.98 (0.77,1.28)

model.1<-glm(HDP~(PFOS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) + ppbmi,
             family =binomial(link = "logit"),
             data=df2)
or<-round(exp(coef(model.1)),2)
or
ci.ll<-round(exp(confint(model.1)),2) [2]
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]
ci.ul
table(model.1$model$HDP)
#0.97 (0.77,1.23)

model.1<-glm(HDP~(PFHxS.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) +  ppbmi,
             family =binomial(link = "logit"),
             data=df2)
or<-round(exp(coef(model.1)),2)
or
ci.ll<-round(exp(confint(model.1)),2) [2]
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]
ci.ul
table(model.1$model$HDP)
#0.85 (0.66,1.1)

model.1<-glm(HDP~(PFNA.iqr) + as.factor(mat_educ) + mat_age + as.factor(parity)  +  as.factor(alc.smoke) +  ppbmi,
             family =binomial(link = "logit"),
             data=df2)
or<-round(exp(coef(model.1)),2)
or
ci.ll<-round(exp(confint(model.1)),2) [2]
ci.ll
ci.ul<-round(exp(confint(model.1)),2) [2,2]
ci.ul
table(model.1$model$HDP)
#1.10 (0.82,1.51)


#mixture for HDP


df.hdp<-c('mat_educ', 
                 'mat_age', 
                 'ppbmi', 
                 'parity', 
                 'alc.smoke', 
                 "log.PFNA", 
                 "log.PFOA", 
                 "log.PFOS", 
                 "log.PFHxS", 
                 'HDP') 

df.mixtures.hdp<-df2[df.hdp]  
df.mixtures.hdp<-df.mixtures.hdp[complete.cases(df.mixtures.hdp),] 


## Set names of exposure variables 
Xmn.chem<-c("log.PFNA", "log.PFOA", "log.PFOS","log.PFHxS")  


Mixture<- qgcomp.noboot(HDP ~ log.PFNA + log.PFOA + log.PFOS +  log.PFHxS +
                          as.factor(mat_educ) + mat_age + as.factor(parity) + as.factor(alc.smoke) + ppbmi,
                        expnms = Xmn.chem,
                        data= df.mixtures.hdp,
                        family=binomial(),
                        q=4)

# Output effect estimates 
exp(round((Mixture $psi),2)) 
exp(round((Mixture $ci.coef),2))
table(df.mixtures.hdp$HDP)


```

## Table S7
Sensitivity analysis estimating risk ratios and 95% confidence intervals for the association between hypertensive disorders of pregnancy and individual PFAS and their mixture among pregnant persons in the Atlanta African American Maternal-Child Cohort, 2014-2020
```{r}
## mixture
 # preeclampsia

Mixture.rr.pe<- qgcomp.glm.boot(preecl ~ log.PFNA + log.PFOA + log.PFOS +  log.PFHxS + 
                          as.factor(mat_educ) + mat_age + as.factor(parity) + as.factor(alc.smoke) + ppbmi, 
                        expnms = Xmn.chem, 
                        data= df.mixtures.preec, 
                        family=binomial(), 
                        seed=200,
                        rr=TRUE,
                        q=4) 


# Output effect estimates  
exp(round((Mixture.rr.pe$psi),2))  
exp(round((Mixture.rr.pe$ci.coef),2)) 
table(df.mixtures.preec$preecl) 



## gestational hypertension 

Mixture.rr.ghtn<- qgcomp.glm.boot(g_htn ~ log.PFNA + log.PFOA + log.PFOS +  log.PFHxS + 
                                  as.factor(mat_educ) + mat_age + as.factor(parity) + as.factor(alc.smoke) + ppbmi, 
                                expnms = Xmn.chem, 
                                data= df.mixtures.ghtn, 
                                family=binomial(), 
                                seed=200,
                                rr=TRUE,
                                q=4) 


# Output effect estimates  
exp(round((Mixture.rr.ghtn$psi),2))  
exp(round((Mixture.rr.ghtn$ci.coef),2)) 
table(df.mixtures.ghtn$g_htn) 



# Preeclampsia 

pfoa.preec <- glm(preecl ~ PFOA.iqr + as.factor(mat_educ) + mat_age  + 
                   as.factor(parity)  +  
                  as.factor(alc.smoke)  + 
                   ppbmi, 
                data = df2, 
                family = poisson(link = "log")) 
tidy(pfoa.preec, exponentiate = TRUE, conf.int = TRUE) 
table(pfoa.preec$model$preecl)

pfos.preec <- glm(preecl ~ PFOS.iqr + as.factor(mat_educ) + mat_age  + 
                    as.factor(parity)  +  
                    as.factor(alc.smoke)  + 
                    ppbmi, 
                  data = df2, 
                  family = poisson(link = "log")) 
tidy(pfos.preec, exponentiate = TRUE, conf.int = TRUE) 
table(pfos.preec$model$preecl)


pfhxs.preec <- glm(preecl ~ PFHxS.iqr + as.factor(mat_educ) + mat_age  + 
                    as.factor(parity)  +  
                    as.factor(alc.smoke)  + 
                    ppbmi, 
                  data = df2, 
                  family = poisson(link = "log")) 
tidy(pfhxs.preec, exponentiate = TRUE, conf.int = TRUE) 
table(pfhxs.preec$model$preecl)

pfna.preec <- glm(preecl ~ PFNA.iqr + as.factor(mat_educ) + mat_age  + 
                     as.factor(parity)  +  
                     as.factor(alc.smoke)  + 
                     ppbmi, 
                   data = df2, 
                   family = poisson(link = "log")) 
tidy(pfna.preec, exponentiate = TRUE, conf.int = TRUE) 
table(pfna.preec$model$preecl)



# Gestational hypertension 


pfoa.ghtn <- glm(g_htn ~ PFOA.iqr + as.factor(mat_educ) + mat_age  + 
                    as.factor(parity)  +  
                    as.factor(alc.smoke)  + 
                    ppbmi, 
                  data = df2, 
                  family = poisson(link = "log")) 
tidy(pfoa.ghtn, exponentiate = TRUE, conf.int = TRUE) 
table(pfoa.ghtn$model$g_htn)

pfos.ghtn <- glm(g_htn ~ PFOS.iqr + as.factor(mat_educ) + mat_age  + 
                    as.factor(parity)  +  
                    as.factor(alc.smoke)  + 
                    ppbmi, 
                  data = df2, 
                  family = poisson(link = "log")) 
tidy(pfos.ghtn, exponentiate = TRUE, conf.int = TRUE) 
table(pfos.ghtn$model$g_htn)


pfhxs.ghtn <- glm(g_htn ~ PFHxS.iqr + as.factor(mat_educ) + mat_age  + 
                     as.factor(parity)  +  
                     as.factor(alc.smoke)  + 
                     ppbmi, 
                   data = df2, 
                   family = poisson(link = "log")) 
tidy(pfhxs.ghtn, exponentiate = TRUE, conf.int = TRUE) 
table(pfhxs.ghtn$model$g_htn)

pfna.ghtn <- glm(g_htn ~ PFNA.iqr + as.factor(mat_educ) + mat_age  + 
                    as.factor(parity)  +  
                    as.factor(alc.smoke)  + 
                    ppbmi, 
                  data = df2, 
                  family = poisson(link = "log")) 
tidy(pfna.ghtn, exponentiate = TRUE, conf.int = TRUE) 
table(pfna.ghtn$model$g_htn)




```

## Table S8
Sensitivity analysis estimating the association between hypertensive disorders of pregnancy and the PFAS mixture, estimated using Weighted Quantile Sum (WQS) regression among pregnant persons in the Atlanta African American Maternal-Child Cohort, 2014-2020
```{r}

# preeclampsia
WQS.preec <- gwqs(preecl ~ wqs + as.factor(mat_educ) + mat_age  +  as.factor(parity)  +   as.factor(alc.smoke)  + ppbmi,  
                            mix_name = Xmn.chem, 
                            data =  df.mixtures.preec,
                            q = 10, 
                            validation = 0.6, 
                            b = 200, 
                            b1_pos = TRUE, 
                            b_constr = FALSE, 
                            family = "binomial", 
                            seed = 2016)
# bar plot
gwqs_barplot(WQS.preec)
# get results
summary(WQS.preec)
# Get ORs 
exp(coef(WQS.preec))
# Get CI
round(exp(confint(WQS.preec)),2)


# gestational hypertension
WQS.ghtn <- gwqs(g_htn ~ wqs + as.factor(mat_educ) + mat_age  +  as.factor(parity)  +   as.factor(alc.smoke)  + ppbmi,  
                  mix_name = Xmn.chem, 
                  data = df.mixtures.ghtn, 
                  q = 10, 
                  validation = 0.6, 
                  b = 200, 
                  b1_pos = TRUE, 
                  b_constr = FALSE, 
                  family = "binomial", 
                  seed = 2016)
# bar plot
gwqs_barplot(WQS.ghtn)
# get results
summary(WQS.ghtn)
# Get ORs 
exp(coef(WQS.ghtn))
# Get CI
round(exp(confint(WQS.ghtn)),2)


#### example on repeated holdout WQS 
rep.hold = lapply(1:100,function(i){ # 100 repetitions
  gwqs(preecl ~ wqs + as.factor(mat_educ) + mat_age  +  as.factor(parity)  +   as.factor(alc.smoke)  + ppbmi,  
       mix_name = Xmn.chem, 
       data = df.mixtures.preec,
       q = 10, 
       validation = 0.6, # 40% trainging data, 60% testing data
       b = 10, # 100 bootstraps recommended, but gWQS runs faster with fewer
       b1_pos = TRUE, 
       b_constr = FALSE, 
       family = "binomial", 
       plots = F, tables = F)})

# Function to compile results from 100 repeated holdouts
f_compile <- function(gWQSresult){ # gWQSresult = gWQS results name for repeated holdout (a list)
  
  # WQS index beta estimates
  tmp1 = map(gWQSresult,"fit") %>% map(tidy) # convert fit results to a dataframe
  tmp1 = map2(tmp1,1:length(tmp1),function(x,y){x$rep=y; return(x)}) # add repetition index number
  tmp1 = do.call("rbind",tmp1) # bind all repetitions together
  tmp1 = subset(tmp1, term=="wqs") # subset results to just the wqs-index estimate
  
  # Chemical weights
  tmp3 = map(gWQSresult,"final_weights") # convert weight results to a dataframe
  tmp3 = map2(tmp3,1:length(tmp3),function(x,y){x$rep.rep=y; return(x)}) # add repetition index number
  tmp3 = do.call("rbind",tmp3) # bind all repetitions together
  tmp3 = reshape(tmp3, timevar="mix_name", idvar="rep.rep", direction="wide") # put weights in wide format
  names(tmp3) = sub(".*\\.", "", names(tmp3)) # remove 'mean_weight.' 
  
  # Merge estimates & weights
  tmp4 = merge(tmp1,tmp3,by="rep") 
  tmp4 <- subset(tmp4, select=-c(term,statistic,std.error,p.value)) # drop unecessary variables
}

# Apply f_compile function to put repeated holdout results into dataframe
rep.hold.df = f_compile(rep.hold)

# Check the WQS index estimate distribution - if not approximately ~N then more repetitions needed
hist(rep.hold.df$estimate)

# Calculate the nonparametric WQS index estimate & 95% CI from repeated holdout sampling distributon
median(rep.hold.df$estimate) 
quantile(rep.hold.df$estimate,0.025) 
quantile(rep.hold.df$estimate,0.975)
## How does this estimate compare to the single and no partition methods?

# Calculate mean weights
colMeans(rep.hold.df[,3:12])

```

## Figure S2
Spearman correlation coefficients between natural log transformed PFAS concentrations in the Atlanta African American Maternal-Child Cohort, 2014-2020 (N=513)
```{r}

corr.vars<-c( 
  "impPFHxS", 
  "impPFOS", 
  "impPFOA", 
  "impPFNA") 
names(df2) 

df.corr<-as.data.frame(df2)[corr.vars] 
df.corr$log.PFHxS<-log(df.corr$impPFHxS)    
df.corr$log.PFOS<-log(df.corr$impPFOS) 
df.corr$log.PFOA<-log(df.corr$impPFOA)     
df.corr$log.PFNA<-log(df.corr$impPFNA) 

names(df.corr) # figure out numbers for new log transformed variables 

df.corr<-df.corr[c(5:8)] # SUBSET OUT LOG TRANSFORMED VARIABLES THAT WERE JUST CREATED 

df.corr<-cor(df.corr,method="spearman",use="complete.obs") 

colnames(df.corr)<-c(  "PFHxS", "PFOS", "PFOA", "PFNA") 

rownames(df.corr)<-c(  "PFHxS", "PFOS", "PFOA", "PFNA") 


corrplot(df.corr, 
         method="number", 
         type = "lower", 
         tl.col = "black") 


```

